%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Senior Humanoid Robotics Teleoperation Engineer} % Job title
    {Sanctuary AI} % Organization
    {Vancouver B.C.} % Location
    {05/2021 - present} % Date(s)
    {
      \begin{cvitems}
        \item {Led the development of the teleoperation stack for various humanoid robot models, incorporating diverse operator measurement hardware such as motion capture systems and exoskeletons to enhance teleoperation capabilities.}
        \item {Created a kinematic retargeting framework to align human and robot geometries, enabling precise manipulations across humanoid robots of different sizes and shapes.}
        \item {Enhanced the operator interface with tactile feedback to improve dexterous manipulation skills.}
        \item {Logged over 250 hours operating three generations of humanoid robots in more than 50 live demonstrations, significantly contributing to fundraising efforts that garnered over \$100 million, and supporting live presentations, documentaries (e.g., Bloomberg), remote operations, data collection, and user acceptance testing.}
        \item {Played a pivotal role in the recruitment, onboarding, and mentoring of new team members, growing the team from 2 to 7 members.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Research Assistant} % Job title
    {BLINC (Bionic Limbs for Improved Natural Control) Lab} % Organization
    {Edmonton, A.B.} % Location
    {01/2021 - 05/2021} % Date(s)
    {
      \begin{cvitems}
        \item {Led design and implementation of a general purpose interface to collect electromyography data, train pattern recognition algorithms, display results, and control prosthetic end effectors in real-time.}
        \item {Prototyped and evaluated a wireless force myography wristband using capacitive sensors to control myoelectric prostheses in real-time using various pattern recognition algorithms (e.g. SVM, NN).}
      \end{cvitems}
    }

  \cventry
    {Test Engineer} % Job title
    {Zaber Technologies} % Organization
    {Vancouver, B.C.} % Location
    {01/2017 - 09/2017} % Date(s)
    {
      \begin{cvitems}
        \item {Developed and completed automated test procedures for high precision actuators to determine specifications such as accuracy, backlash, and repeatability with resolution as low as 10 microns.}
        \item {Designed, purchased, and constructed all electrical and software systems required to fully automate a thrust-speed test setup rated up to 1000 lbs using a combination of Python, Arduino, and PID control techniques.}
        \item {Gained hands-on experience independently operating CNC mills, CNC waterjet cutters, laser cutters, manual lathes, and many other machining techniques.}
      \end{cvitems}
    }

  \cventry
    {Control Systems Researcher} % Job title
    {University of Alberta} % Organization
    {Edmonton, A.B.} % Location
    {05/2016 - 09/2016} % Date(s)
    {
      \begin{cvitems}
        \item {Independently designed and constructed both a single and double self-balancing inverted pendulum apparatus to demonstrate and apply different control theory techniques such as PID and LQR controllers.}
        \item {Created a customized real-time GUI to monitor all variables corresponding to the pendulum to compare controllers and speed up debugging.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
