%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-skyblue}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}
% \definecolor{sectiondivider}{HTML}{5D5D5D}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

%-------------------------------------------------------------------------------
\begin{document}

\input{info.tex}

%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
  {Recruitment Team}
  {Figure AI\\Sunnyvale, CA}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Job Application for Teleop Software Engineer}
% How the letter is opened
\letteropening{Dear Recruitment Team,}
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter

% Print the title with above letter information
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}

\lettersection{About Me}

I am a passionate robotics engineer with a strong foundation in mechatronics. 
My background in mechanical engineering is enriched with skills in software, controls, and networking, gained through both academic study and professional experience. 
I am committed to further developing my technical expertise to emerge as a leader in the robotics field.
\\\\Over the past three years at Sanctuary AI, I have implemented teleoperation techniques for three generations of humanoid robots. 
As the initial member of the teleoperation team, I played a key role in its growth and the evolution of our software stack.
My experience in operating humanoid robots has provided me with valuable insights into optimizing hardware capabilities.

\lettersection{Why Figure AI?}
Figure AI has consistently demonstrated technical leadership in robotics, showcasing impressive autonomous behavior that has attracted significant funding. 
This infusion of resources positions the company to make substantial advancements in the field of humanoid robotics. 
I am eager to take the next step in my career by transitioning into a leadership role, where I can balance my technical expertise with leadership responsibilities.

\lettersection{Why Me?}
I possess expertise in motion capture systems, virtual reality, haptics, kinematic retargeting, and dexterous finger control, with a strong foundation in modern C++ for implementing these technologies. 
My adaptable, generalist skill set and motivation to learn new skills is well-suited for the rapidly evolving field of humanoid robotics, enabling me to effectively respond to and integrate state-of-the-art advancements.
My experience in designing teleoperation systems for humanoid robots positions me as an ideal candidate to enhance Figure's teleoperation initiatives. 

\end{cvletter}

%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter information
\makeletterclosing

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
  {Eric Wells ~~~·~~~Cover Letter}
  {\thepage}

\end{document}
